### 2016-11-09 thesis/intro/intro.tex
tmp commit

When a satiety-controlling hormone, such as leptin, reaches the arcuate nucleus region of the hypothalamus, it can stimulate or inhibit orexogenic, anorexogenic, or both neurons.
Depending on which neurons are stimulated or inhibited, the hormone will ultimately alter the satiety level of the individual.

Firstly, when an orexogenic \gls{npy}/\gls{agrp} neurons are stimulated,

>>>>

When a satiety-controlling hormone such as leptin reaches the arcuate nucleus region of the hypothalamus, it can stimulate or inhibit orexogenic, anorexogenic, or both orexogenic and anorexogenic neurons.
Depending on which neurons are stimulated or inhibited, the hormone will ultimately alter the satiety level of the individual.\\

\noindent
Both \gls{pomc} and \gls{cart} are strong anorexogenic neuropeptides that stimulate the downstream effector neurons via the \gls{mc4r} pathway \citep{Barsh2002}.

\gls{pomc} is a precursor protein that is cleaved to produce adrenocorticotropin (ACTH), $\alpha$-, $\beta$- and $\gamma$-\gls{msh}, and $\beta$-endorphin (citation Smith1988, endocr. rev.).
Perhaps the most important, or most relevant, in the context of obesity and satiety control is the $\alpha$-MSH.
$\alpha$-MSH is the main ligand that binds to the \gls{mc4r} expressed in the brain, and sends anorexogenic signals to the downstream neurons through this pathway \citep{Krude1998}.

Similarly, \gls{cart} is also a neuropeptide that has a strong anorexogenic effect discovered by (citation Kristensen1998 on CART).
Unlike $\alpha$-MSH, the receptor for \gls{cart} has not been identified yet, and the exact mechanism in which \gls{cart} acts is unclear (citation... Kristensen1998, Rogge2008).

Since the expression of both neuropeptides are under the control of leptin, and that $\alpha$-MSH is known to stimulate the melanocortin pathway to produce an anorexogenic signal to the downstream neurons, this satiety-controlling signalling pathway is known as the leptin-melanocortin pathway.
\\

\noindent
In contrast to the \gls{pomc}/\gls{cart} neurons, orexogenic neuropeptides \gls{npy} and \gls{agrp} are produced in the \gls{npy}/\gls{agrp} neurons when stimulated by hormones that control satiety.

\gls{npy} was first discovered by \citet{Tatemoto1982}, and later associated with altered eating behaviour in rats by \citet{Clark1984}.
\gls{npy} is recognised by the \gls{nyr}, a G protein-coupled receptor expressed on the downstream effector neurons, which relays the orexogenic signal from the \gls{npy}/\gls{agrp} neurons (citation, Herzog 1992 PNAS) \citep{Barsh2002, Bell2005}

Agouti protein is a protein normally expressed in the skin where it affects the pigmentation, and was first identified over 100 years ago by \citet{Castle1910} in mice that had yellow, or agouti-coloured coat.
Although the fact that ubiquitous expression of agouti protein caused obesity in mice was known for a long time, the biochemical mechanism that caused such phenotype was not elucidated until 1997 by \citet{Ollmann1997}.
In brief, \gls{agrp} was shown to be a strong antagonist of the \gls{mc4r}, expressed in the downstream neurons to the \gls{npy}/\gls{agrp} neurons, and thus inhibited the anorexogenic signalling through the melanocortin pathway \citep{Barsh2002,Ollmann1997}.\\

\noindent
Together, \gls{npy}/\gls{agrp} and \gls{pomc}/\gls{cart} neurons produce contrasting signals that affect the overall satiety of the individual.
Depending on how strong or weak these signals are, the individual may be more or less susceptible to obesity.
